Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-04-13 paper.Rnw
Fix up layout of ADNI automated methods survey table

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                Discussion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tabulation of segmentation accuracies of existing methods (ADNI)
%
<<ADNI1-literature, echo=F, results="asis",cache=FALSE>>=
tab = read.csv("data/ADNI-existing-work.csv")
tab$Notes <- NULL

@@

latex(adni_lit, file="", 
      size="scriptsize",
      caption="Caption", 
      rowname=NULL,
      col.just=c("p{1.5in}l","p{0.5in}","p{.5in}","p{1in}"),
      title="")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                Discussion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tabulation of segmentation accuracies of existing methods (ADNI)
%
<<ADNI1-literature, echo=F, results="asis",cache=FALSE>>=
caption = paste(
  "Survey of automated segmentation accuracy of the ADNI dataset",
  sep=" ")

tab = read.csv("data/ADNI-existing-work.csv")
tab$Notes <- NULL

@@

latex(adni_lit, file="", 
      size="scriptsize",
      caption=caption, 
      rowname=NULL,
      col.just=c("p{1.5in}l","p{0.5in}","p{1.3in}","p{1.5in}"),
      title="")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
